\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Estimating Trending Topics on Twitter with Small Subsets of the Total Data}

### 2015-01-13 paper.tex
minor paper changes

For each hashtag, the kernel sketch stores a positive value between $0$ and $2$ (though typically $\leq 1$) that approximates how often the hashtag showed up in the past. In \nref{sec:Correctness} we will show that this aggregate Count-Min sketch weights the hashtags that occurred $i > 0$ days ago with weight approximately $\frac{1}{i}$.

@@

Therefore, summing over all hashtags that increment counters in position $b$ gives $\overline{M}(x)$ for all hashtags that occurred on $z$-unit $t$, and within a factor $4$ of $\sum\limits_{i=1}^T \frac{1}{i}*$(value for $x$ in a Count-Min sketch using the same hash functions for all hashtags occurring $i > 0$ $z$-units ago). 
\end{proof}
This value is approximately (frequency in last $y$-unit) / (freq current $z$-unit + $\sum\limits_{i=1}^T \frac{1}{i} *$ (frequency of hashtag $i$ $z$-units ago)).
This seems to be a desirable function to maximize since it finds hashtags that are common in the last $y$-unit that have been comparatively infrequent in the past. This function is good since it especially emphasizes hashtags that are different than those seen in the past few $z$-units.  This ensures that the same items do not stay trending for too long.

@@

The History requires $O(md)$ space for each Count-Min sketch, so it requires a total of $O(md*\log(T))$ space.
Each node in the heap requires a constant amount of space, so the heap requires $O(s)$ space.
The hash table always contains at most $s$ entries with each entry requiring a constant amount of space.  Also, in order to maintain an expected $O(1)$ lookup time, the hash table needs to have $O(s)$ bins.  Thus, the hash table requires $O(s)$ space.
The queue requires an entry for every hashtag still in the current window, so it requires $O(x)$ space.

>>>>

For each hashtag, the kernel sketch stores a positive value that approximates how often the hashtag showed up in the past. In \nref{sec:Correctness} we will show that this aggregate Count-Min sketch weights the hashtags that occurred $i > 0$ days ago with weight approximately $\frac{1}{i}$.

@@

Therefore, summing over all hashtags that increment counters in position $b$ gives $\overline{M}(x)$ for all hashtags that occurred on $z$-unit $t$, and within a factor $4$ of $\sum\limits_{i=1}^T \frac{1}{i}*$(value for $x$ in a Count-Min sketch using the same hash functions for all hashtags occurring $i > 0$ $z$-units ago). 
\end{proof}

Given this proof and the fact that Count-Min sketches return approximate frequency counts, we know the priority function to be approximately:
\begin{equation} 
\label{eq:approxpriority}
\textbf{priority}(\textnormal{hashtag}) \approx \frac{\textbf{freq}(\textnormal{hashtag}, \textnormal{present } y \textnormal{-unit})}{\textbf{freq}(\textnormal{hashtag}, \textnormal{present } z \textnormal{-unit}) + \sum\limits_{i=1}^T \frac{1}{i}* \textbf{freq}(\textnormal{hashtag}, i \ z \textnormal{-units ago})}
\end{equation}
%This value is approximately (frequency in last $y$-unit) / (freq current $z$-unit + $\sum\limits_{i=1}^T \frac{1}{i} *$ (frequency of hashtag $i$ $z$-units ago)).
This seems to be a desirable function to maximize since it finds hashtags that are common in the last $y$-unit that have been comparatively infrequent in the past. This function is good since it especially emphasizes hashtags that are different than those seen in the past few $z$-units.  This ensures that the same items do not stay trending for too long.

@@

The History requires $O(md)$ space for each Count-Min sketch, so it requires a total of $O(md*\log(T))$ space.
Each node in the heap requires a constant amount of space, so the heap requires $O(s)$ space.
The hash table always contains at most $s$ entries with each entry requiring a constant amount of space.  Also, in order to maintain an expected $O(1)$ lookup time, the hash table needs to have $O(s)$ bins.  Thus, the hash table requires $O(s)$ space.
The queue requires an entry for every hashtag seen in the last $y$-unit, so it requires $O(x)$ space.
